### 2014-11-11 contract-language.tex
Merged changes from contract-language of paper

\begin{figure}
\vspace{-7pt}
\begin{smathpar}
\begin{array}{rclcl}
\multicolumn{5}{c}{
  {x,y,\cureff} \in \mathtt{EffVar} \qquad \qquad
  {\sf Op} \in \mathtt{OperName}
}\\
\cv 		& \in & \mathtt{Contract} 	& \coloneqq & \forall (x : \tau).\cv
        \ALT \forall x.\cv \ALT \pi \\
\tau		& \in	& \mathtt{EffType}	& \coloneqq &  {\sf Op}
        \ALT \tau \vee \tau \\
\pi			&	\in & \mathtt{Prop} & \coloneqq & \true \ALT R(x,y)
        \ALT \pi \vee \pi \\
			  & 		&	 &  \ALT & \pi \wedge \pi \ALT \pi \Rightarrow \pi \\
R				& \in & \mathtt{Relation}	& \coloneqq & \visZ \ALT \soZ
        \ALT \sameobjZ \ALT R^+ \\
				&			&	 &  \ALT & R \cup R \ALT R \cap R \\
\end{array}
\end{smathpar}
\caption{Contract language.}
\label{fig:contract-lang}
\end{figure}

@@

The classification scheme, presented formally in Figure~\ref{sem:classify},
defines rules to judge the consistency class of a contact. For example, the
scheme classifies the \cf{getBalance} contract ($\cv_{gb}$) from
\S~\ref{sec:motivation} as a {\sf\small CausallyConsistent} contract, because
the sequent $\Delta \vdash \ccc \Rightarrow \cv_{gb}$ is valid in first-order
logic (therefore, $\cv_{gb} \le \ccc$), whereas the sequent $\Delta \vdash \ecc
\Rightarrow \cv_{gb}$ is invalid (therefore, $\cv_{gb} \not\le \ecc$). Since we
confine our contract language to a decidable subset of the logic, validity
of such sequents can be decided mechanically allowing us to automate the
classification scheme in \name.

@@

The theorem states that if a data store correctly enforces $\scc$, $\ccc$, and
$\ecc$ contracts in all well-formed executions, then the same store, extended
with the classification scheme shown in Figure~\ref{sem:classify}, can enforce
all well-formed \name contracts. The proof of the theorem is given in the
supplementary material\footnote{The supplementary material also provides the
concrete reduction rules for enforcing the consistency classes.}.

>>>>

\begin{figure}
\begin{smathpar}
\begin{array}{rclcl}
\multicolumn{5}{c}{
  {x,y,\cureff} \in \mathtt{EffVar} \qquad \qquad
  {\sf Op} \in \mathtt{OperName}
}\\
\cv 		& \in & \mathtt{Contract} 	& \coloneqq & \forall (x : \tau).\cv
        \ALT \pi \\
\tau		& \in	& \mathtt{EffType}	& \coloneqq &  {\sf Op}
        \ALT \tau \vee \tau \\
\pi			&	\in & \mathtt{Prop} & \coloneqq & \true \ALT R(x,y)
        \ALT \pi \vee \pi \\
			  & 		&	 &  \ALT & \pi \wedge \pi \ALT \pi \Rightarrow \pi \\
R				& \in & \mathtt{Relation}	& \coloneqq & \visZ \ALT \soZ
        \ALT \sameobjZ \ALT R^+ \\
				&			&	 &  \ALT & R \cup R \ALT R \cap R \\
\end{array}
\end{smathpar}
\caption{Contract language.}
\label{fig:contract-lang}
\end{figure}

@@

The classification scheme, presented formally in Figure~\ref{sem:classify},
defines rules to judge the consistency class of a contact. For example, the
scheme classifies the \cf{getBalance} contract ($\cv_{gb}$) from
\S~\ref{sec:motivation} as a {\sf\small CausallyConsistent} contract, because
the sequent $\Delta \vdash \ccc \Rightarrow \cv_{gb}$ is valid in first-order
logic (therefore, $\cv_{gb} \le \ccc$), whereas the sequent $\Delta \vdash \ecc
\Rightarrow \cv_{gb}$ is invalid (therefore, $\cv_{gb} \not\le \ecc$). Since we
confine of our contract language to a decidable subset of the logic, validity
of such sequents can be decided mechanically allowing us to automate the
classification scheme in \name.

@@

\noindent The theorem states that if a data store correctly enforces $\scc$,
$\ccc$, and $\ecc$ contracts in all well-formed executions, then the same
store, extended with the classification scheme shown in
Figure~\ref{sem:classify}, can enforce all well-formed \name contracts. The
proof of the theorem is given below:

\begin{proof}
  Hypothesis:
  \begin{smathpar}
  \begin{array}{cr}
    \auxred{} {\E,\langle op,\tau \rangle;\sigma \pll \Sigma} {\eff}
    {\E', \sigma \pll \Sigma} & H\npp\\
    \E' \models \cv_\tau[\eff/\cureff] & H\npp\\
  \end{array}
  \end{smathpar}
  Since $\tau$ is the contract class of $\cv$, by inversion, we have
  $\cv \le \cv_\tau$. By the definition of $\le$ relation:
  \begin{smathpar}
  \begin{array}{cr}
    \Delta \vdash \forall \cureff. \cv_\tau \Rightarrow \cv & H\npp\\
  \end{array}
  \end{smathpar}
   Since $\eff$ denotes new effect, it is a fresh variable that does
   not occur free in $\Delta$. From $H3$, after instantiating bound
   $\cureff$ with $\eff$, we have:
  \begin{smathpar}
  \begin{array}{cr}
    \Delta \vdash \cv_\tau[\eff/\cureff] \Rightarrow \cv[\eff/\cureff]
      & H\npp\\
  \end{array}
  \end{smathpar}
  Due to the soundness of natural deduction for first-order logic,
  $H4$ implies that for all models $\mathcal{M}$ such that
  $\mathcal{M} \models \Delta$, if $\mathcal{M} \models
  \cv_\tau[\eff/\cureff]$ then $\mathcal{M} \models
  \cv[\eff/\cureff]$. Since $\E'$ is well-formed, we have:
  \begin{smathpar}
  \begin{array}{cr}
    \E' \models \Delta & H\npp\\
  \end{array}
  \end{smathpar}
  Proof follows from $H1$, $H5$, and $H4$.
  \qed
\end{proof}

It is important to note that Theorem~\ref{thm:classification-sound}
does not ascribe any semantics to the reduction relation
($\xrightarrow{}$). As such, it makes no assumptions about how the
store actually implements ${\sf ec}$, ${\sf cc}$ and ${\sf sc}$
guarantees. The specific implementation strategy is determined by the
operational semantics of the store, which \emph{defines} the reduction
relation for that particular store. The following section describes
operational semantics of the store used by the \name implementation.
